The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
reflow intro

###
Results and interpretation of temporal scale - balh

Results and interpretation of spatial scale - blah blah

Results and interpretation of social scale - blah blah blah

## Perspectives  to advance multilayer networks

### Habitat selection and space use

Mayor et al. 2009 paper

MRSF Laforge paper

van Beest et al. 2014 scale paper

1st/2nd/3rd order selection blah blah

Paper: Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1

Multi-scale habitat selection modeling: a review and outlook

>>>>

###
Results and interpretation of temporal scale

Results and interpretation of spatial scale

Results and interpretation of social scale

## Perspectives  to advance multilayer networks 
### Habitat selection and space use

* Mayor et al. 2009 paper 
* MRSF Laforge paper 
* van Beest et al. 2014 scale paper 
* 1st/2nd/3rd order selection
* Habitat–performance relationships: finding the right metric at a given spatial scale Jean-Michel Gaillard1,*, Mark Hebblewhite2, Anne Loison3, Mark Fuller4, Roger Powell5, Mathieu Basille1,6 and Bram Van Moorter1
* Multi-scale habitat selection modeling: a review and outlook
